Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures

### 2025-05-21 CCGRID Presentation/main.tex
fixes: 7 workflow -> 7 workflows, HEFT-* valid for all -> HEFT-MM valid for all (slide 20)
changed "worse" to "surplus"

    \begin{itemize}
        \item Respects processor memory sizes
        \begin{itemize}
            \item HEFTM-\textbf{BL} and HEFTM-\textbf{BLC} produce valid makespans that are only $10$-$35\%$ worse than invalid HEFT makespans
            \item HEFTM-\textbf{MM} able to schedule all workflows even under extreme memory constraint
        \end{itemize}

@@

        \begin{itemize}  
        \item Workflows
        \begin{itemize}
             \item Real-world workflows
            \item Generated with WFGen [7] from 7 workflow: sizes from 1K to 30K tasks
            \item Divided in groups by size
        \end{itemize}

@@

    \begin{tikzpicture}[remember picture, overlay]
            \node[
                fill=white,
                draw=black,
                rounded corners,
                minimum width=4cm,
                minimum height=1.5cm,
                align=center
            ] at ([xshift=-5cm,yshift=-4.2cm]current page.north east)
            {HEFTM-* makespans valid, HEFT not \\ HEFTM-BL and BLC : 10 - 35\% worse \\ HEFTM-MM makespans 40\% to 2x worse};
        \end{tikzpicture}

@@

          \begin{tikzpicture}[remember picture, overlay]
        \node[
            fill=white,
            draw=black,
            rounded corners,
            minimum width=4cm,
            minimum height=1.5cm,
            align=center
        ] at ([xshift=-3.5cm,yshift=-5.5cm]current page.north east)
        {HEFT invalid over 100 tasks \\ HEFTM-BL / HEFTM-BLC invalid over  \\8000 tasks
        \\ HEFTM-* valid for all workflows };
    \end{tikzpicture}

@@

\begin{itemize}
    \item Extend an influential predecessor (HEFT)
    \item Memory-aware, communicate over communication buffers
    \item Valid makespans, only 10-35\% worse than invalid HEFT makespans
    \item HEFTM-\textbf{MM} proves unique resilience in memory-constrained scenario
\end{itemize}

\pause
    \begin{table}[ht]
        \centering
        \setlength{\tabcolsep}{12pt} % adjust horizontal padding between columns
        \renewcommand{\arraystretch}{1.3} % increase row height for readability
        \begin{tabular}{|p{6.5cm}|p{2.5cm}|}
            \hline
            \textbf{Scenario} & \textbf{Winner} \\
            \hline
            Memory very constrained & HEFTM-\textbf{MM} \\
            Memory somewhat constrained, need smallest makespan & HEFTM-\textbf{BL} \\
            Need balance, willing to trade (very little) makespan for less memory requirement & HEFTM-\textbf{BLC} \\
            Lots of memory, need smallest makespan & \only<1>{HEFT?} \only<2> {\sout{HEFT} ~~~~~~~ HEFTM-\textbf{BL}} \\
            \hline
        \end{tabular}
    \end{table}

>>>>

    \begin{itemize}
        \item Respects processor memory sizes
        \begin{itemize}
            \item HEFTM-\textbf{BL} and HEFTM-\textbf{BLC} produce valid makespans with just $10$-$35\%$ surplus over invalid HEFT makespans
            \item HEFTM-\textbf{MM} able to schedule all workflows even under extreme memory constraint
        \end{itemize}

@@

        \begin{itemize}  
        \item Workflows
        \begin{itemize}
             \item Real-world workflows
            \item Generated with WFGen [7] from 7 workflows: sizes from 1K to 30K tasks
            \item Divided in groups by size
        \end{itemize}

@@

    \begin{tikzpicture}[remember picture, overlay]
            \node[
                fill=white,
                draw=black,
                rounded corners,
                minimum width=4cm,
                minimum height=1.5cm,
                align=center
            ] at ([xshift=-5cm,yshift=-4.2cm]current page.north east)
            {HEFTM-* makespans valid, HEFT not \\ HEFTM-BL and BLC : 10 - 35\% surplus \\ HEFTM-MM makespans 40\% to 2x surplus};
        \end{tikzpicture}

@@

          \begin{tikzpicture}[remember picture, overlay]
        \node[
            fill=white,
            draw=black,
            rounded corners,
            minimum width=4cm,
            minimum height=1.5cm,
            align=center
        ] at ([xshift=-3.5cm,yshift=-5.5cm]current page.north east)
        {HEFT invalid over 100 tasks \\ HEFTM-BL / HEFTM-BLC invalid over  \\8000 tasks
        \\ HEFTM-MM valid for all workflows };
    \end{tikzpicture}

@@

\begin{itemize}
    \item Extend an influential predecessor (HEFT)
    \item Memory-aware, communicate over communication buffers
    \item Valid makespans, only 10-35\% surplus over invalid HEFT makespans
    \item HEFTM-\textbf{MM} proves unique resilience in memory-constrained scenario
\end{itemize}

\pause
    \begin{table}[ht]
        \centering
        \setlength{\tabcolsep}{12pt} % adjust horizontal padding between columns
        \renewcommand{\arraystretch}{1.3} % increase row height for readability
        \begin{tabular}{|p{6.5cm}|p{2.8cm}|}
            \hline
            \textbf{Scenario} & \textbf{Recommendation} \\
            \hline
            Memory very constrained & HEFTM-\textbf{MM} \\
            Memory somewhat constrained, need smallest makespan & HEFTM-\textbf{BL} \\
            Need balance, willing to trade (very little) makespan for less memory requirement & HEFTM-\textbf{BLC} \\
            Lots of memory, need smallest makespan & \only<1>{HEFT?} \only<2> {\sout{HEFT} ~~~~~~~ HEFTM-\textbf{BL}} \\
            \hline
        \end{tabular}
    \end{table}
